Measuring the Price of Anarchy in Critical Care Unit Interactions

### 2014-12-09 Paper/paper.tex
Have regions fixed in intro section

Throughout this paper it is assumed that both CCUs (NH and RG) act selfishly and rationally.
The strategies of each CCU are capacity thresholds at which they declare being in ``diversion''. When in ``diversion'' the arrival rates of patients are modified.
Given the proximity of the two CCUs, one CCU could for example divert their patients to the other.
Figure \ref{arrivalrateregions} shows a diagrammatic representation of this where $\lambda_h^{(r)}$ for $h\in\{\NH, \RG\}$ and $r\in\{(l,l), (l,h), (h,l), (h,h)\}$ simply denote arrival rates that will be defined for both models considered in Section \ref{results}, where $a,b,c \text{ and } d$ are regions with boundaries defined by the capacity thresholds.
It is also assumed that diverted patients will be treated under the length of stay profile of the CCU they are admitted to.
The capacity thresholds are denoted as $K_{h}\in\mathbb{Z}$ for $h\in\{\NH,\RG\}$. Note that $0\leq K_h\leq c_h$.

\begin{figure}[!htbp]
\begin{center}
    \begin{tikzpicture}
        \draw  (0,0) rectangle (4,3);
        \draw [dashed, red, thick] (0,1) -- (4,1);
        \draw [dashed, red, thick] (3,0) -- (3,3);
        \node at (-.5,1) {$K_{\NH}$};
        \node at (3,3.25) {$K_{\RG}$};
        \node at (1.5,2) {$\lambda_{h}^{(a)}$};
        \node at (3.5,2) {$\lambda_{h}^{(b)}$};
        \node at (1.5,.5) {$\lambda_{h}^{(c)}$};
        \node at (3.5,.5) {$\lambda_{h}^{(d)}$};
    \end{tikzpicture}
\caption{General arrival rates for each CCU at each region, where $h\in\{\NH, \RG\}$} \label{arrivalrateregions}
\end{center}
\end{figure}

>>>>

Throughout this paper it is assumed that both CCUs (NH and RG) act selfishly and rationally.
The strategies of each CCU are capacity thresholds at which they declare being in ``diversion''. When in ``diversion'' the arrival rates of patients are modified.
Given the proximity of the two CCUs, one CCU could for example divert their patients to the other.
Figure \ref{arrivalrateregions} shows a diagrammatic representation of this where $\lambda_h^{r}$ for $h\in\{\NH, \RG\}$ and $r\in\{(l,l), (l,h), (h,l), (h,h)\}$ simply denote arrival rates that will be defined for both models considered in Section \ref{results}, where $r$ denotes regions with boundaries defined by the capacity thresholds.
For example $(l,h)$ denotes a region for which $\NH$ experiences \textit{low} demand and $\RG$ experiences \textit{high} demand.
It is also assumed that diverted patients will be treated under the length of stay profile of the CCU they are admitted to.
The capacity thresholds are denoted as $K_{h}\in\mathbb{Z}$ for $h\in\{\NH,\RG\}$. Note that $0\leq K_h\leq c_h$.

\begin{figure}[!htbp]
\begin{center}
    \begin{tikzpicture}
        \draw  (0,0) rectangle (4,3);
        \draw [dashed, red, thick] (0,1) -- (4,1);
        \draw [dashed, red, thick] (3,0) -- (3,3);
        \node at (-.5,1) {$K_{\NH}$};
        \node at (3,3.25) {$K_{\RG}$};
        \node at (1.5,2) {$\lambda_{h}^{(l,l)}$};
        \node at (3.5,2) {$\lambda_{h}^{(l,h)}$};
        \node at (1.5,.5) {$\lambda_{h}^{(h,l)}$};
        \node at (3.5,.5) {$\lambda_{h}^{(h,h)}$};
    \end{tikzpicture}
\caption{General arrival rates for each CCU at each region, where $h\in\{\NH, \RG\}$} \label{arrivalrateregions}
\end{center}
\end{figure}
